GOV 1006: Milestone 8

### 2020-04-22 milestone8.Rmd
update with milestone 8

---
title: "GOV 1006: Milestone 7"
subtitle: "Paper Replication"
author: "Pieter Quinton"
date: "4/17/2020"
abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government and their satisfaction with democracy. I was able to completely replicate the majority of his findings aside from a summary table of the data. My extension evaluates how consistent or long-term unemployment may impact one's views. Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions."
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
document_class: article
bibliography: milestone5_bib.bib
---

@@

## Introduction

The paper I have chosen for my replication project is entitled "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" (@bauer2018). ^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is availabe through [bookdown](https://bookdown.org/pquinton/milestone7/milestone7.pdf).] It was authored by Paul C. Bauer in 2018. The purpose of the paper is to evaluate how unemployment affects a person's trust in the government and their views towards democracy in general. Bauer begins with macro level data from the Netherlands and Switzerland to construct his analysis but expands to utilize panel data so as to evaluate the relationship on an individual level.

The aim of Bauer's paper is to show how unemployment influences a person's trust in government, satisfaction with democracy, and life satisfaction in general. Bauer also controls for variations in age, education, and party membership. Because the link between life satisfaction and unemployment is somewhat more widely studied, Bauer uses that as a base metric to evaluate the magnitude of the other effects upon. All three dependent variables (trust in government, satisfaction in democracy, and life satisfaction) are measured on a 1-10 scale with 0 indicating no trust or satisfaction and 10 indicating complete trust or satisfaction.

Bauer finds that there is no consistent effect between unemployment and trust in the government or satisfaction with democracy. These findings contradict his initial hypothesis that unemployment would lead people to have lower levels of trust and satisfaction with the government and democratic institutions. However, Bauer does find that unemployment is negatively related to life satisfaction. People who are unemployed are generally less satisfied with their lives than those who are employed. This finding is consistent with previous research on the topic. Moving forward, Bauer hopes to increase the sample size of the studied group to further explore heterogenous treatment effects across various subgroups of individuals. For example, he hypothesizes that the effect of unemployment on attitudes may be greater among people traditionally disadvantaged in the labor market such as women and workers of a lower-class.

## Literature Review

@@

## Replication

@@

## Extension

@@

@@

## Conclusion

@@

## References

>>>>

---
title: "GOV 1006: Milestone 8"
subtitle: "Paper Replication"
author: "Pieter Quinton"
date: "4/17/2020"
abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government and their satisfaction with democracy. I was able to completely replicate the majority of his findings aside from a summary table of the data. My extension evaluates how consistent or long-term unemployment may impact one's views. Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions."
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
document_class: article
bibliography: milestone5_bib.bib
mainfont: Wingdings
sansfont: Wingdings
fontsize: 12pt
---

@@

# Introduction

"Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation", authored by Paul Bauer, explores how unemployment affects a person's trust in the government and their views towards democracy in general (@bauer2018). Bauer utilizes panel data from two household surveys, one in Switzerland and one in the Netherlands, to evaluate the relationship between unemployment and feelings towards government on an individual level. Due to prior findings on the link between life satisfaction and unemployment, Bauer uses that as a base metric to evaluate the magnitude of the other effects upon. Bauer finds that a household's unemployment status has no consistent effect on either trust in the government or satisfaction with democracy. These findings contradict his initial hypothesis that unemployment would lead people to have lower levels of trust and satisfaction with the government and democratic institutions. However, Bauer does find that unemployment is negatively associated with life satisfaction. People who are unemployed are generally less satisfied with their lives than those who are employed. This finding is consistent with previous research on the topic (@hudson2006; @jimeno2007). Moving forward, Bauer hopes to increase the sample size of the studied group to further explore heterogenous treatment effects across various subgroups of individuals. For example, he hypothesizes that the effect of unemployment on attitudes may be greater among people traditionally disadvantaged in the labor market such as women and workers of a lower-class.

Starting with the replication materials provided by Bauer through the Harvard Dataverse, I worked to replicate the findings of Bauer's paper (@dataverse).^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is available through [bookdown](https://bookdown.org/pquinton/milestone7/milestone7.pdf).] As Bauer did, I conducted my replication and subsequent extension in RStudio (@RStudio). Thanks to Bauer well documented code and use of RStudio, my replication process was relatively straight forward though there were a couple of discrepencies which I will go into in further detail in the "Replication" section of this paper.

# Literature Review

@@

# Replication

@@

# Extension

@@

My findings largely confirmed Bauer's. The interaction term between unemployment in the present year and unemployment in the previous year was not statistically significant. The lack of statistical significance indicates that the aggregation of two years of unemployment does not create significant impacts on one's views towards government and democracy. However, in the dataset from Switzerland (SHP) there was a statistically significant negative relationship between satisfaction with democracy and lagged unemployment. This relationship is only present in the pooled model and the fixed effects model. Because the relationship between lagged unemployment and satisfaction with democracy is not present in the weighted fixed effects model which is supposed to be the most robust model, it is unclear how strong that finding is.

@@

# Conclusion

@@

# References
